Paper Report

### 2017-12-05 Paper_report.tex
Save

\subsection{Main idea}
\textbf{Auto-evaluation metric without reference.}
This research is that attention distribution becomes a confidence metric (Translation quality and Decoder confidence)
\begin{itemize}
\item Filtering out bad translation from a large back-translated corpus (Provide a better parallel corpus)
\item Selecting the best translation in a hybrid setup of 2 translation systems
\end{itemize}
The result is that this metric could be consider as an human judgement (Not so true!, just about 50\%) and leads to BLEU score improvement (in some cases).

@@

	\end{itemize}
\item Refinement procedure (Solution for rare words that GAN does not well solve) repeats until reaching stopping condition.
	\begin{enumerate}
	\item Extracting a synthetic high-quality dictionary (Most frequent words) evaluated by CSLS
	\item Applying Procrustes solution for generating more accurate dictionary.
	\end{enumerate}
\item Stopping condition/Best hyper-parameters selection - Validation step: Similarity measure CSLS between mapped source and target words.\\
	Why: It is based on K-NN and overcomes a problem of two spaces and "Hubs and Anti-hubs" (Some points are highly near many other points while there are some points are not nearest any point in high-dimensional spaces).\\
	They proposed a bipartite neighbourhood graph. Each word of a language is connected to K words of an other language.
	\begin{equation}
	CSLS(Wx_{s}, y_{t}) = 2 \cos(Wx_{s}, y_{t}) - r_{T}(Wx_{s}) - r_{S}(y_{t})
	\end{equation}
		\begin{itemize}
		\item $r_{T}(Wx_{s}) = \frac{1}{K} \sum_{y_{t} \in N_{T}(Wx_{s})} \cos(Wx_{s}, y_{t})$\\
		Mean similarity of a source embedding $x_{s}$ to its target neighbours.
		\item $r_{S}(y_{t}) = \frac{1}{K} \sum_{Wx_{s} \in N_{S}(y_{t})} \cos(y_{t}, Wx_{s})$\\
		Mean similarity of a source embedding $x_{s}$ to its target neighbours.
		\item $N_{T}(Wx_{s})$: Neighbour of a source word $Wx_{s}$ in target word space.
		\end{itemize}

@@

\subsection{}

@@

\subsection{Loss in unsupervised learning} 
\begin{equation}
loss(\theta) = max(0 , 1 - \sum_{(\textbf{f}^+,\textbf{e}^+) \in T} E_{\Phi} [s_{\theta} (\textbf{a}|\textbf{f}^+, \textbf{e}^+)]  + \sum_{(\textbf{f}^+,\textbf{e}^-) \in \Omega} E_{\Phi} [s_{\theta} (\textbf{a}|\textbf{f}^+, \textbf{e}^-)] )
\label{Tamura14recurrent Loss Unsupervised Learning}
\end{equation}
where
\begin{itemize}
\item T: Training data (Bilingual sentences) as Observed data
\item $\Omega$ : Full translation search space as neighbourhood of observe data, .
\item $\Phi$ : Set of all possible alignments given (\textbf{e},\textbf{f})
\item $E_{\Phi} [s_{\theta}]$ : Expected value of the scores $s_\theta$ on $\Phi$
\item $e^+$ : A target language sentence in T
\item $e^-$ : A pseudo-target language sentence
\item $\sum_{(\textbf{f}^+,\textbf{e}^+) \in T} E_{\Phi} [s_{\theta} (\textbf{a}|\textbf{f}^+, \textbf{e}^+)]$ : Expectation term for observed data
\item$ \sum_{(\textbf{f}^+,\textbf{e}^-) \in \Omega} E_{\Phi} [s_{\theta} (\textbf{a}|\textbf{f}^+, \textbf{e}^-)] )$ : Expectation term for neighbourhood
\end{itemize}

@@

\section{Hierarchical Multiscale Recurrent Neural Networks}

\subsection{Main idea}
Hierarchical Multiscale RNNs learns the latent hierarchical structure of a sequence and its temporal representation with non-fixed timescales (Without explicit boundary information).

@@

The advantages of "Multiscale" over standard RNNs:
\begin{itemize}
\item Updating the high-level layers is less frequently $\rightarrow$ Computational efficiency and Vanishing gradient problem. Solving vanishing gradient problem means that this model could delivering efficiently long-term dependencies.
\item Flexible resource allocation. The model could modify the number of hidden units for an information. For example, the model could use more units to the higher layers (Long-term dependency) and less units to the lower layers (Short-term dependency). This means that it could decide to keep the long-term or short-term information.

@@

\item Hierarchical RNNs with Known explicit hierarchical boundary structure (Not multiscale).\\ Problem: It is the same with Clockwork RNNs that boundary information is not explicit and expensive to be discovered.

@@

\subsection{Update mechanism}
They describe Hierarchical Multiscale RNN (HM-RNN) based on LSTM update rule. It is better to see the graph in paper.\\
\marginpar{Why it is not based on RNN ?}

@@

@@

From now, the work of translation is modelling $p(f_1^J|e_1^I)$. Our work is more complicated by adding an alignment component $a_1^J$ which maps from a source position j to a target position $a_j$ (It could be i, but there is also empty words).

>>>>

\subsection{Main idea}
\textbf{Auto-evaluation metric without reference.}
This research is that attention distribution becomes a confidence metric (Translation quality and Decoder confidence)
\begin{itemize}
\item Filtering out bad translation from a large back-translated corpus (Provide a better parallel corpus)
\item Selecting the best translation in a hybrid setup of 2 translation systems
\end{itemize}
The result is that this metric could be consider as an human judgment (Not so true!, just about 50\%) and leads to BLEU score improvement (in some cases).

@@

	\end{itemize}
\item Refinement procedure (Solution for rare words that GAN does not well solve) repeats until reaching stopping condition.
	\begin{enumerate}
	\item Extracting a synthetic high-quality dictionary (Most frequent words) evaluated by CSLS
	\item Applying Procrustes solution for generating more accurate dictionary.
	\end{enumerate}
\item Stopping condition/Best hyper-parameters selection - Validation step: Similarity measure CSLS between mapped source and target words.\\
	Why: It is based on K-NN and overcomes a problem of two spaces and "Hubs and Anti-hubs" (Some points are highly near many other points while there are some points are not nearest any point in high-dimensional spaces).\\
	They proposed a bipartite neighborhood graph. Each word of a language is connected to K words of an other language.
	\begin{equation}
	CSLS(Wx_{s}, y_{t}) = 2 \cos(Wx_{s}, y_{t}) - r_{T}(Wx_{s}) - r_{S}(y_{t})
	\end{equation}
		\begin{itemize}
		\item $r_{T}(Wx_{s}) = \frac{1}{K} \sum_{y_{t} \in N_{T}(Wx_{s})} \cos(Wx_{s}, y_{t})$\\
		Mean similarity of a source embedding $x_{s}$ to its target neighbors.
		\item $r_{S}(y_{t}) = \frac{1}{K} \sum_{Wx_{s} \in N_{S}(y_{t})} \cos(y_{t}, Wx_{s})$\\
		Mean similarity of a source embedding $x_{s}$ to its target neighbors.
		\item $N_{T}(Wx_{s})$: Neighbor of a source word $Wx_{s}$ in target word space.
		\end{itemize}

@@

\subsection{How to train these two model ?}
\begin{itemize}
\item Two models are:
\begin{equation}
\begin{split}
&p_1(x,z; \theta_1) = p(e)p(a,f| e; \theta_1)  \\
&p_2(x,z; \theta_2) = p(f)p(a,e| f; \theta_2)
\end{split}
\end{equation}
where \\
$x = (e,f)$ is an input sentence pair, \\
$z = {z_{i,j} \in \{0,1\} : 1 \leq i \leq I, 1 \leq j \leq J}$ is a set of indicator variables for each potential alignment edge.

\item The data likelihood:
\begin{equation}
\prod_x p_k(x; \theta_k) = \prod_x \sum_z p_k(x,z, \theta_k)
\end{equation}
where $k \in {1, 2}$ is models.

\item \textbf{Joint objective function} is maximizing the data likelihood:
\begin{equation}
\max_{\theta_1, \theta_2} \sum_x [log p_1(x;\theta_1) + log p_2(x;\theta_2)] \\
\end{equation}
Because of the probability that two models agree the alignments on an example $x$ being
\begin{equation}
\sum_z p_1(z
|x;\theta_1) p_2(z|x; \theta_2)
\end{equation}

\item Therefore,
\begin{equation}
\max_{\theta_1, \theta_2} \sum_x [log p_1(x;\theta_1) + log p_2(x;\theta_2) + log\sum_z p_1(z
|x;\theta_1) p_2(z|x; \theta_2)]
\end{equation}
\end{itemize}

\subsubsection{Optimization via EM}
From the standard EM,
\begin{equation}
\begin{split}
& E: q(z;x) := p(z|x ;\theta) \\
& M: \theta^{'} := argmax_{\theta} \sum_{x,z} q(z;x) \quad log \,  p(x,z;\theta)
\end{split}
\end{equation}

becomes

\begin{equation}
\begin{split}
& E: q(z;x) := \frac{1}{Z_x} p_1(z|x ;\theta_1) p_2(z|x ;\theta_2) \\
& M: \theta^{'} := argmax_{\theta} \sum_{x,z} q(z;x) \, log \,  p_1(x,z;\theta_1) +  \sum_{x,z} q(z;x) \, log \,  p_2(x,z;\theta_2)
\end{split}
\end{equation}

where $Z_x$ is a normalization constant. It is sum of the product of two model posteriors over the set of possible $z$ with nonzero probability under both models.\\

In E-step,
\begin{equation}
 E: q(z;x) := \frac{1}{Z_x} p_1(z|x ;\theta_1) p_2(z|x ;\theta_2)
\end{equation}

becomes

\begin{equation}
q(z;x) := \prod_{i,j} p_1(z_{ij} | x; \theta_1) \, p_2(z_{ij} | x; \theta_2)
\end{equation}
where each $p_k(z_{i,j}|x; \theta_k)$ is the posterior marginal probability of the (i,j) edge.\\

This posterior $q(z;x)$ could show the disagreement because this product $p_1(z|x ;\theta_1) p_2(z|x ;\theta_2)$ is small.

\subsection{Analysis}
This agreement approach does not guarantee to increase the joint objective. The experiment shows that it could provide an effective method of achieving model agreement and a significant accuracy gains over independent training.

@@

\subsection{Loss in unsupervised learning} 
\begin{equation}
loss(\theta) = max(0 , 1 - \sum_{(\textbf{f}^+,\textbf{e}^+) \in T} E_{\Phi} [s_{\theta} (\textbf{a}|\textbf{f}^+, \textbf{e}^+)]  + \sum_{(\textbf{f}^+,\textbf{e}^-) \in \Omega} E_{\Phi} [s_{\theta} (\textbf{a}|\textbf{f}^+, \textbf{e}^-)] )
\label{Tamura14recurrent Loss Unsupervised Learning}
\end{equation}
where
\begin{itemize}
\item T: Training data (Bilingual sentences) as Observed data
\item $\Omega$ : Full translation search space as neighborhood of observe data, .
\item $\Phi$ : Set of all possible alignments given (\textbf{e},\textbf{f})
\item $E_{\Phi} [s_{\theta}]$ : Expected value of the scores $s_\theta$ on $\Phi$
\item $e^+$ : A target language sentence in T
\item $e^-$ : A pseudo-target language sentence
\item $\sum_{(\textbf{f}^+,\textbf{e}^+) \in T} E_{\Phi} [s_{\theta} (\textbf{a}|\textbf{f}^+, \textbf{e}^+)]$ : Expectation term for observed data
\item$ \sum_{(\textbf{f}^+,\textbf{e}^-) \in \Omega} E_{\Phi} [s_{\theta} (\textbf{a}|\textbf{f}^+, \textbf{e}^-)] )$ : Expectation term for neighborhood
\end{itemize}

@@

\section{Hierarchical Multiscale Recurrent Neural Networks \citep{Chung2016Hierarchical}}

\subsection{Main idea}
Hierarchical Multi-scale RNNs learns the latent hierarchical structure of a sequence and its temporal representation with non-fixed timescales (Without explicit boundary information).

@@

The advantages of "Multi-scale" over standard RNNs:
\begin{itemize}
\item Updating the high-level layers is less frequently $\rightarrow$ Computational efficiency and Vanishing gradient problem. Solving vanishing gradient problem means that this model could delivering efficiently long-term dependencies.
\item Flexible resource allocation. The model could modify the number of hidden units for an information. For example, the model could use more units to the higher layers (Long-term dependency) and less units to the lower layers (Short-term dependency). This means that it could decide to keep the long-term or short-term information.

@@

\item Hierarchical RNNs with Known explicit hierarchical boundary structure (Not multi-scale).\\ Problem: It is the same with Clockwork RNNs that boundary information is not explicit and expensive to be discovered.

@@

\subsection{Update mechanism}
They describe Hierarchical Multi-scale RNN (HM-RNN) based on LSTM update rule. It is better to see the graph in paper.\\
\marginpar{Why it is not based on RNN ?}

@@

%----------------------------------------------------------------------------------------
%	Hybrid Neural Network alignment and Lexicon Model in direct HMM for Statistical Machine Translation
%----------------------------------------------------------------------------------------

\section{Hybrid Neural Network alignment and Lexicon Model in direct HMM for Statistical Machine Translation}

@@

From now, the work of translation is modeling $p(f_1^J|e_1^I)$. Our work is more complicated by adding an alignment component $a_1^J$ which maps from a source position j to a target position $a_j$ (It could be i, but there is also empty words).
